\section{Module \ocamlinlinecode{Oxcaml}}\label{Oxcaml}%
\label{Oxcaml--val-f}\ocamlcodefragment{\ocamltag{keyword}{val} f : int \ocamltag{arrow}{$\rightarrow$} ('a.\allowbreak{} \ocamltag{type-var}{'a} \ocamltag{arrow}{$\rightarrow$} \ocamltag{type-var}{'a}) \ocamltag{arrow}{$\rightarrow$} unit}\begin{ocamlindent}Polymorphic arguments require parentheses\end{ocamlindent}%
\medbreak
Unboxed types have a trailing hash '\#'

\label{Oxcaml--type-pt}\ocamlcodefragment{\ocamltag{keyword}{type} pt = \{}\\
\begin{ocamltabular}{p{1.000\textwidth}}\ocamlinlinecode{x : int;\allowbreak{}}\label{Oxcaml--type-pt.x}\\
\ocamlinlinecode{y : float32\#;\allowbreak{}}\label{Oxcaml--type-pt.y}\\
\end{ocamltabular}%
\\
\ocamlcodefragment{\}}\\
\label{Oxcaml--type-segment}\ocamlcodefragment{\ocamltag{keyword}{type} segment = \{}\\
\begin{ocamltabular}{p{1.000\textwidth}}\ocamlinlinecode{start : \hyperref[Oxcaml--type-pt]{\ocamlinlinecode{pt\#}};\allowbreak{}}\label{Oxcaml--type-segment.start}\\
\ocamlinlinecode{stop : \hyperref[Oxcaml--type-pt]{\ocamlinlinecode{pt\#}};\allowbreak{}}\label{Oxcaml--type-segment.stop}\\
\end{ocamltabular}%
\\
\ocamlcodefragment{\}}\\
\subsection{Layouts\label{Oxcaml--layouts}}%
\label{Oxcaml--type-t_any}\ocamlcodefragment{\ocamltag{keyword}{type} t\_\allowbreak{}any : any}\begin{ocamlindent}Layout \ocamlinlinecode{any}.\end{ocamlindent}%
\medbreak
\label{Oxcaml--type-t_value_or_null}\ocamlcodefragment{\ocamltag{keyword}{type} t\_\allowbreak{}value\_\allowbreak{}or\_\allowbreak{}null : value\_\allowbreak{}or\_\allowbreak{}null}\begin{ocamlindent}Layout \ocamlinlinecode{value\_\allowbreak{}or\_\allowbreak{}null}.\end{ocamlindent}%
\medbreak
\label{Oxcaml--type-t_float64}\ocamlcodefragment{\ocamltag{keyword}{type} t\_\allowbreak{}float64 : float64}\begin{ocamlindent}Layout \ocamlinlinecode{float64}.\end{ocamlindent}%
\medbreak
\label{Oxcaml--type-t_float32}\ocamlcodefragment{\ocamltag{keyword}{type} t\_\allowbreak{}float32 : float32}\begin{ocamlindent}Layout \ocamlinlinecode{float32}.\end{ocamlindent}%
\medbreak
\label{Oxcaml--type-t_word}\ocamlcodefragment{\ocamltag{keyword}{type} t\_\allowbreak{}word : word}\begin{ocamlindent}Layout \ocamlinlinecode{word}.\end{ocamlindent}%
\medbreak
\label{Oxcaml--type-t_bits64}\ocamlcodefragment{\ocamltag{keyword}{type} t\_\allowbreak{}bits64 : bits64}\begin{ocamlindent}Layout \ocamlinlinecode{bits64}.\end{ocamlindent}%
\medbreak
\label{Oxcaml--type-t_bits32}\ocamlcodefragment{\ocamltag{keyword}{type} t\_\allowbreak{}bits32 : bits32}\begin{ocamlindent}Layout \ocamlinlinecode{bits32}.\end{ocamlindent}%
\medbreak
\label{Oxcaml--type-t_vec128}\ocamlcodefragment{\ocamltag{keyword}{type} t\_\allowbreak{}vec128 : vec128}\begin{ocamlindent}Layout \ocamlinlinecode{vec128}.\end{ocamlindent}%
\medbreak
\label{Oxcaml--type-t_void}\ocamlcodefragment{\ocamltag{keyword}{type} t\_\allowbreak{}void : void}\begin{ocamlindent}Layout \ocamlinlinecode{void}.\end{ocamlindent}%
\medbreak
\subsection{Kind abbreviations\label{Oxcaml--kind-abbreviations}}%
\label{Oxcaml--type-t_value}\ocamlcodefragment{\ocamltag{keyword}{type} t\_\allowbreak{}value}\begin{ocamlindent}\ocamlinlinecode{value} is the default kind, so the annotation is not rendered.\end{ocamlindent}%
\medbreak
\label{Oxcaml--type-t_immediate}\ocamlcodefragment{\ocamltag{keyword}{type} t\_\allowbreak{}immediate : immediate}\begin{ocamlindent}Kind abbreviation \ocamlinlinecode{immediate}.\end{ocamlindent}%
\medbreak
\label{Oxcaml--type-t_immediate64}\ocamlcodefragment{\ocamltag{keyword}{type} t\_\allowbreak{}immediate64 : immediate64}\begin{ocamlindent}Kind abbreviation \ocamlinlinecode{immediate64}.\end{ocamlindent}%
\medbreak
\label{Oxcaml--type-t_immutable_data}\ocamlcodefragment{\ocamltag{keyword}{type} t\_\allowbreak{}immutable\_\allowbreak{}data : immutable\_\allowbreak{}data}\begin{ocamlindent}Kind abbreviation \ocamlinlinecode{immutable\_\allowbreak{}data}.\end{ocamlindent}%
\medbreak
\label{Oxcaml--type-t_sync_data}\ocamlcodefragment{\ocamltag{keyword}{type} t\_\allowbreak{}sync\_\allowbreak{}data : sync\_\allowbreak{}data}\begin{ocamlindent}Kind abbreviation \ocamlinlinecode{sync\_\allowbreak{}data}.\end{ocamlindent}%
\medbreak
\label{Oxcaml--type-t_mutable_data}\ocamlcodefragment{\ocamltag{keyword}{type} t\_\allowbreak{}mutable\_\allowbreak{}data : mutable\_\allowbreak{}data}\begin{ocamlindent}Kind abbreviation \ocamlinlinecode{mutable\_\allowbreak{}data}.\end{ocamlindent}%
\medbreak
\subsection{Kind annotations with modalities\label{Oxcaml--kind-annotations-with-modalities}}%
\label{Oxcaml--type-t_portable}\ocamlcodefragment{\ocamltag{keyword}{type} t\_\allowbreak{}portable : value \ocamltag{keyword}{mod} portable}\begin{ocamlindent}Kind annotation with a modality.\end{ocamlindent}%
\medbreak
\label{Oxcaml--type-t_contended}\ocamlcodefragment{\ocamltag{keyword}{type} t\_\allowbreak{}contended : value \ocamltag{keyword}{mod} contended}\begin{ocamlindent}Kind annotation with a different modality.\end{ocamlindent}%
\medbreak
\label{Oxcaml--type-t_multi_mod}\ocamlcodefragment{\ocamltag{keyword}{type} t\_\allowbreak{}multi\_\allowbreak{}mod : value \ocamltag{keyword}{mod} portable contended}\begin{ocamlindent}Kind annotation with multiple modalities.\end{ocamlindent}%
\medbreak
\label{Oxcaml--type-t_everything}\ocamlcodefragment{\ocamltag{keyword}{type} t\_\allowbreak{}everything : float64 \ocamltag{keyword}{mod} everything}\begin{ocamlindent}The \ocamlinlinecode{everything} bounds abbreviation.\end{ocamlindent}%
\medbreak
\subsection{Kind annotations on parameterized types\label{Oxcaml--kind-annotations-on-parameterized-types}}%
\label{Oxcaml--type-imm_param}\ocamlcodefragment{\ocamltag{keyword}{type} ('a : immediate) imm\_\allowbreak{}param}\begin{ocamlindent}A type parameter with a kind constraint.\end{ocamlindent}%
\medbreak
\label{Oxcaml--type-float_param}\ocamlcodefragment{\ocamltag{keyword}{type} ('a : float64) float\_\allowbreak{}param}\begin{ocamlindent}A type parameter with a different kind constraint.\end{ocamlindent}%
\medbreak
\label{Oxcaml--type-multi_kind}\ocamlcodefragment{\ocamltag{keyword}{type} (('a : immediate),\allowbreak{} ('b : float64)) multi\_\allowbreak{}kind}\begin{ocamlindent}Multiple kind-constrained parameters.\end{ocamlindent}%
\medbreak
\subsection{Kind annotations with \ocamlinlinecode{with} constraints\label{Oxcaml--kind-annotations-with-with-constraints}}%
\label{Oxcaml--type-t_with}\ocamlcodefragment{\ocamltag{keyword}{type} 'a t\_\allowbreak{}with : immediate \ocamltag{keyword}{with} \ocamltag{type-var}{'a}}\begin{ocamlindent}Kind annotation with a \ocamlinlinecode{with} constraint.\end{ocamlindent}%
\medbreak
\label{Oxcaml--type-t_with_modalities}\ocamlcodefragment{\ocamltag{keyword}{type} 'a t\_\allowbreak{}with\_\allowbreak{}modalities : immutable\_\allowbreak{}data \ocamltag{keyword}{with} \ocamltag{type-var}{'a} @@ portable contended}\begin{ocamlindent}Kind annotation with a \ocamlinlinecode{with} constraint and modalities.\end{ocamlindent}%
\medbreak
\subsection{Kind annotations on type aliases\label{Oxcaml--kind-annotations-on-type-aliases}}%
\label{Oxcaml--type-t_alias}\ocamlcodefragment{\ocamltag{keyword}{type} t\_\allowbreak{}alias : immediate = int}\begin{ocamlindent}Has both a kind annotation and a manifest.\end{ocamlindent}%
\medbreak
\subsection{Kind-constrained polymorphism in values\label{Oxcaml--kind-constrained-polymorphism-in-values}}%
\label{Oxcaml--val-poly_immediate}\ocamlcodefragment{\ocamltag{keyword}{val} poly\_\allowbreak{}immediate : ('a : immediate).\allowbreak{} \ocamltag{type-var}{'a} \ocamltag{arrow}{$\rightarrow$} \ocamltag{type-var}{'a}}\begin{ocamlindent}Kind constraint on a polymorphic type variable.\end{ocamlindent}%
\medbreak
\label{Oxcaml--val-poly_float64}\ocamlcodefragment{\ocamltag{keyword}{val} poly\_\allowbreak{}float64 : ('a : float64).\allowbreak{} \ocamltag{type-var}{'a} \ocamltag{arrow}{$\rightarrow$} \ocamltag{type-var}{'a}}\begin{ocamlindent}Kind constraint on a polymorphic type variable with a different kind.\end{ocamlindent}%
\medbreak
\subsection{Parenthesization of product kinds\label{Oxcaml--parenthesization-of-product-kinds}}%
\label{Oxcaml--type-t_many_modalities}\ocamlcodefragment{\ocamltag{keyword}{type} t\_\allowbreak{}many\_\allowbreak{}modalities : value \ocamltag{keyword}{mod} global aliased many contended portable forkable unyielding immutable stateless external\_\allowbreak{}}\begin{ocamlindent}A \ocamlinlinecode{mod} kind annotation with many modalities.\end{ocamlindent}%
\medbreak
\label{Oxcaml--type-t_outer_mod}\ocamlcodefragment{\ocamltag{keyword}{type} t\_\allowbreak{}outer\_\allowbreak{}mod : (float64 \& immediate) \ocamltag{keyword}{mod} portable}\begin{ocamlindent}Should render as \ocamlinlinecode{(float64 \& immediate) mod portable}.\end{ocamlindent}%
\medbreak
\label{Oxcaml--type-t_inner_mod}\ocamlcodefragment{\ocamltag{keyword}{type} t\_\allowbreak{}inner\_\allowbreak{}mod : float64 \& (immediate \ocamltag{keyword}{mod} portable)}\begin{ocamlindent}Should render as \ocamlinlinecode{float64 \& (immediate mod portable)}.\end{ocamlindent}%
\medbreak
\subsection{Kind abbreviations\label{Oxcaml--kind-abbreviations_2}}%
\label{Oxcaml--type-t_abbrev}\ocamlcodefragment{\ocamltag{keyword}{type} t\_\allowbreak{}abbrev : my\_\allowbreak{}abbrev \ocamltag{keyword}{mod} immutable}\begin{ocamlindent}A type with an abbreviated kind.\end{ocamlindent}%
\medbreak
\subsection{Zero alloc\label{Oxcaml--zero-alloc}}%
\label{Oxcaml--val-add}\ocamlcodefragment{\ocamltag{keyword}{val} add : bool \ocamltag{arrow}{$\rightarrow$} int \ocamltag{arrow}{$\rightarrow$} int \ocamltag{arrow}{$\rightarrow$} int [@@zero\_\allowbreak{}alloc]}\begin{ocamlindent}Zero allocation bindings have an extension attribute attached. See https://oxcaml.org/documentation/miscellaneous-extensions/zero\_alloc\_check/\end{ocamlindent}%
\medbreak
\label{Oxcaml--val-add_opt}\ocamlcodefragment{\ocamltag{keyword}{val} add\_\allowbreak{}opt : bool \ocamltag{arrow}{$\rightarrow$} int \ocamltag{arrow}{$\rightarrow$} int \ocamltag{arrow}{$\rightarrow$} int [@@zero\_\allowbreak{}alloc opt]}\begin{ocamlindent}Like \ocamlinlinecode{add} but with an \ocamlinlinecode{opt} attribute.\end{ocamlindent}%
\medbreak
\label{Oxcaml--val-add_strict}\ocamlcodefragment{\ocamltag{keyword}{val} add\_\allowbreak{}strict : bool \ocamltag{arrow}{$\rightarrow$} int \ocamltag{arrow}{$\rightarrow$} int \ocamltag{arrow}{$\rightarrow$} int [@@zero\_\allowbreak{}alloc strict]}\begin{ocamlindent}Like \ocamlinlinecode{add} but with a \ocamlinlinecode{strict} attribute.\end{ocamlindent}%
\medbreak
\label{Oxcaml--val-add_strict_opt}\ocamlcodefragment{\ocamltag{keyword}{val} add\_\allowbreak{}strict\_\allowbreak{}opt : bool \ocamltag{arrow}{$\rightarrow$} int \ocamltag{arrow}{$\rightarrow$} int \ocamltag{arrow}{$\rightarrow$} int [@@zero\_\allowbreak{}alloc strict opt]}\begin{ocamlindent}Like \ocamlinlinecode{add} but with a \ocamlinlinecode{strict} and \ocamlinlinecode{opt} attributes.\end{ocamlindent}%
\medbreak
\label{Oxcaml--val-add_opt_strict}\ocamlcodefragment{\ocamltag{keyword}{val} add\_\allowbreak{}opt\_\allowbreak{}strict : bool \ocamltag{arrow}{$\rightarrow$} int \ocamltag{arrow}{$\rightarrow$} int \ocamltag{arrow}{$\rightarrow$} int [@@zero\_\allowbreak{}alloc strict opt]}\begin{ocamlindent}Like \ocamlinlinecode{add} but with a \ocamlinlinecode{strict} and \ocamlinlinecode{opt} attributes in reverse order.\end{ocamlindent}%
\medbreak
\label{Oxcaml--val-alt_syntax}\ocamlcodefragment{\ocamltag{keyword}{val} alt\_\allowbreak{}syntax : int \ocamltag{arrow}{$\rightarrow$} int [@@zero\_\allowbreak{}alloc]}\begin{ocamlindent}Alternative syntax for zero alloc annotation\end{ocamlindent}%
\medbreak
\label{Oxcaml--val-curried_zero_alloc}\ocamlcodefragment{\ocamltag{keyword}{val} curried\_\allowbreak{}zero\_\allowbreak{}alloc : int \ocamltag{arrow}{$\rightarrow$} int \ocamltag{arrow}{$\rightarrow$} int [@@zero\_\allowbreak{}alloc arity 1]}\begin{ocamlindent}Function that returns a function that is \ocamlinlinecode{zero\_\allowbreak{}alloc}.\end{ocamlindent}%
\medbreak
\subsection{Modalities\label{Oxcaml--modalities}}%
\label{Oxcaml--type-opaque}\ocamlcodefragment{\ocamltag{keyword}{type} opaque}\\
\label{Oxcaml--type-modalities_all}\ocamlcodefragment{\ocamltag{keyword}{type} modalities\_\allowbreak{}all = \{}\begin{ocamlindent}\ocamlinlinecode{f\_\allowbreak{}global : \hyperref[Oxcaml--type-opaque]{\ocamlinlinecode{opaque}} @@ global;\allowbreak{}}\label{Oxcaml--type-modalities_all.f_global}%
\begin{ocamlindent}Locality modality.\end{ocamlindent}%
\ocamlinlinecode{f\_\allowbreak{}local : \hyperref[Oxcaml--type-opaque]{\ocamlinlinecode{opaque}};\allowbreak{}}\label{Oxcaml--type-modalities_all.f_local}%
\begin{ocamlindent}Locality modality (local is not rendered).\end{ocamlindent}%
\ocamlinlinecode{f\_\allowbreak{}unique : \hyperref[Oxcaml--type-opaque]{\ocamlinlinecode{opaque}};\allowbreak{}}\label{Oxcaml--type-modalities_all.f_unique}%
\begin{ocamlindent}Uniqueness modality (unique is not rendered).\end{ocamlindent}%
\ocamlinlinecode{f\_\allowbreak{}aliased : \hyperref[Oxcaml--type-opaque]{\ocamlinlinecode{opaque}} @@ aliased;\allowbreak{}}\label{Oxcaml--type-modalities_all.f_aliased}%
\begin{ocamlindent}Uniqueness modality.\end{ocamlindent}%
\ocamlinlinecode{f\_\allowbreak{}many : \hyperref[Oxcaml--type-opaque]{\ocamlinlinecode{opaque}} @@ many;\allowbreak{}}\label{Oxcaml--type-modalities_all.f_many}%
\begin{ocamlindent}Linearity modality.\end{ocamlindent}%
\ocamlinlinecode{f\_\allowbreak{}once : \hyperref[Oxcaml--type-opaque]{\ocamlinlinecode{opaque}};\allowbreak{}}\label{Oxcaml--type-modalities_all.f_once}%
\begin{ocamlindent}Linearity modality (once is not rendered).\end{ocamlindent}%
\ocamlinlinecode{f\_\allowbreak{}portable : \hyperref[Oxcaml--type-opaque]{\ocamlinlinecode{opaque}} @@ portable;\allowbreak{}}\label{Oxcaml--type-modalities_all.f_portable}%
\begin{ocamlindent}Portability modality.\end{ocamlindent}%
\ocamlinlinecode{f\_\allowbreak{}nonportable : \hyperref[Oxcaml--type-opaque]{\ocamlinlinecode{opaque}};\allowbreak{}}\label{Oxcaml--type-modalities_all.f_nonportable}%
\begin{ocamlindent}Portability modality (nonportable is not rendered).\end{ocamlindent}%
\ocamlinlinecode{f\_\allowbreak{}uncontended : \hyperref[Oxcaml--type-opaque]{\ocamlinlinecode{opaque}};\allowbreak{}}\label{Oxcaml--type-modalities_all.f_uncontended}%
\begin{ocamlindent}Contention modality (uncontended is not rendered).\end{ocamlindent}%
\ocamlinlinecode{f\_\allowbreak{}contended : \hyperref[Oxcaml--type-opaque]{\ocamlinlinecode{opaque}} @@ contended;\allowbreak{}}\label{Oxcaml--type-modalities_all.f_contended}%
\begin{ocamlindent}Contention modality.\end{ocamlindent}%
\ocamlinlinecode{f\_\allowbreak{}unyielding : \hyperref[Oxcaml--type-opaque]{\ocamlinlinecode{opaque}} @@ unyielding;\allowbreak{}}\label{Oxcaml--type-modalities_all.f_unyielding}%
\begin{ocamlindent}Yield modality.\end{ocamlindent}%
\ocamlinlinecode{f\_\allowbreak{}yielding : \hyperref[Oxcaml--type-opaque]{\ocamlinlinecode{opaque}};\allowbreak{}}\label{Oxcaml--type-modalities_all.f_yielding}%
\begin{ocamlindent}Yield modality (yielding is not rendered).\end{ocamlindent}%
\ocamlinlinecode{f\_\allowbreak{}forkable : \hyperref[Oxcaml--type-opaque]{\ocamlinlinecode{opaque}} @@ forkable;\allowbreak{}}\label{Oxcaml--type-modalities_all.f_forkable}%
\begin{ocamlindent}Fork modality.\end{ocamlindent}%
\ocamlinlinecode{f\_\allowbreak{}unforkable : \hyperref[Oxcaml--type-opaque]{\ocamlinlinecode{opaque}};\allowbreak{}}\label{Oxcaml--type-modalities_all.f_unforkable}%
\begin{ocamlindent}Fork modality (unforkable is not rendered).\end{ocamlindent}%
\ocamlinlinecode{f\_\allowbreak{}stateless : \hyperref[Oxcaml--type-opaque]{\ocamlinlinecode{opaque}} @@ stateless;\allowbreak{}}\label{Oxcaml--type-modalities_all.f_stateless}%
\begin{ocamlindent}Statefulness modality.\end{ocamlindent}%
\ocamlinlinecode{f\_\allowbreak{}stateful : \hyperref[Oxcaml--type-opaque]{\ocamlinlinecode{opaque}};\allowbreak{}}\label{Oxcaml--type-modalities_all.f_stateful}%
\begin{ocamlindent}Statefulness modality (stateful is not rendered).\end{ocamlindent}%
\ocamlinlinecode{f\_\allowbreak{}immutable : \hyperref[Oxcaml--type-opaque]{\ocamlinlinecode{opaque}} @@ immutable;\allowbreak{}}\label{Oxcaml--type-modalities_all.f_immutable}%
\begin{ocamlindent}Visibility modality.\end{ocamlindent}%
\ocamlinlinecode{f\_\allowbreak{}read\_\allowbreak{}write : \hyperref[Oxcaml--type-opaque]{\ocamlinlinecode{opaque}};\allowbreak{}}\label{Oxcaml--type-modalities_all.f_read_write}%
\begin{ocamlindent}Visibility modality (read\_write is not rendered).\end{ocamlindent}%
\ocamlinlinecode{f\_\allowbreak{}no\_\allowbreak{}modality : \hyperref[Oxcaml--type-opaque]{\ocamlinlinecode{opaque}};\allowbreak{}}\label{Oxcaml--type-modalities_all.f_no_modality}%
\begin{ocamlindent}No modality, for reference.\end{ocamlindent}%
\end{ocamlindent}%
\ocamlcodefragment{\}}\\
\subsection{Multiple modalities on a field\label{Oxcaml--multiple-modalities-on-a-field}}%
\label{Oxcaml--type-modalities_multi}\ocamlcodefragment{\ocamltag{keyword}{type} modalities\_\allowbreak{}multi = \{}\\
\begin{ocamltabular}{p{0.500\textwidth}p{0.500\textwidth}}\ocamlinlinecode{a : \hyperref[Oxcaml--type-opaque]{\ocamlinlinecode{opaque}} @@ global portable;\allowbreak{}}\label{Oxcaml--type-modalities_multi.a}& Field with \ocamlinlinecode{global portable} modalities.\\
\end{ocamltabular}%
\\
\ocamlcodefragment{\}}\\
\subsection{Modalities on tuple and function fields\label{Oxcaml--modalities-on-tuple-and-function-fields}}%
\label{Oxcaml--type-modalities_tuple}\ocamlcodefragment{\ocamltag{keyword}{type} modalities\_\allowbreak{}tuple = \{}\\
\begin{ocamltabular}{p{0.500\textwidth}p{0.500\textwidth}}\ocamlinlinecode{f : int * string @@ portable;\allowbreak{}}\label{Oxcaml--type-modalities_tuple.f}& Tuple field with modality.\\
\end{ocamltabular}%
\\
\ocamlcodefragment{\}}\\
\label{Oxcaml--type-modalities_fn}\ocamlcodefragment{\ocamltag{keyword}{type} modalities\_\allowbreak{}fn = \{}\\
\begin{ocamltabular}{p{0.500\textwidth}p{0.500\textwidth}}\ocamlinlinecode{g : int \ocamltag{arrow}{$\rightarrow$} int @@ portable;\allowbreak{}}\label{Oxcaml--type-modalities_fn.g}& Function field with modality.\\
\end{ocamltabular}%
\\
\ocamlcodefragment{\}}\\
\subsection{Modalities on constructor arguments\label{Oxcaml--modalities-on-constructor-arguments}}%
\label{Oxcaml--type-modalities_cstr}\ocamlcodefragment{\ocamltag{keyword}{type} modalities\_\allowbreak{}cstr = }\begin{ocamlindent}\ocamlcodefragment{| \ocamltag{constructor}{A} \ocamltag{keyword}{of} string @@ global}\label{Oxcaml--type-modalities_cstr.A}%
\begin{ocamlindent}Constructor argument with \ocamlinlinecode{global} modality.\end{ocamlindent}%
\ocamlcodefragment{| \ocamltag{constructor}{B} \ocamltag{keyword}{of} int \ocamltag{arrow}{$\rightarrow$} int @@ portable}\label{Oxcaml--type-modalities_cstr.B}%
\begin{ocamlindent}Function constructor argument with modality.\end{ocamlindent}%
\ocamlcodefragment{| \ocamltag{constructor}{C} \ocamltag{keyword}{of} int * string @@ portable}\label{Oxcaml--type-modalities_cstr.C}%
\begin{ocamlindent}Tuple constructor argument with modality.\end{ocamlindent}%
\ocamlcodefragment{| \ocamltag{constructor}{D} \ocamltag{keyword}{of} int @@ portable * string @@ global}\label{Oxcaml--type-modalities_cstr.D}%
\begin{ocamlindent}Per-element modalities in a constructor tuple.\end{ocamlindent}%
\ocamlcodefragment{| \ocamltag{constructor}{E} \ocamltag{keyword}{of} \{}\\
\begin{ocamltabular}{p{1.000\textwidth}}\ocamlinlinecode{x : int @@ portable;\allowbreak{}}\label{Oxcaml--type-modalities_cstr.x}\\
\ocamlinlinecode{y : string @@ global;\allowbreak{}}\label{Oxcaml--type-modalities_cstr.y}\\
\end{ocamltabular}%
\\
\ocamlcodefragment{\}}\label{Oxcaml--type-modalities_cstr.E}%
\begin{ocamlindent}Per-element modalities in a constructor record.\end{ocamlindent}%
\ocamlcodefragment{| \ocamltag{constructor}{F}}\label{Oxcaml--type-modalities_cstr.F}%
\begin{ocamlindent}Constant constructor.\end{ocamlindent}%
\end{ocamlindent}%
\label{Oxcaml--type-modalities_gadt}\ocamlcodefragment{\ocamltag{keyword}{type} 'a modalities\_\allowbreak{}gadt = }\begin{ocamlindent}\ocamlcodefragment{| \ocamltag{constructor}{A} : string @@ global \ocamltag{arrow}{$\rightarrow$} [ `a ] \hyperref[Oxcaml--type-modalities_gadt]{\ocamlinlinecode{modalities\_\allowbreak{}gadt}}}\label{Oxcaml--type-modalities_gadt.A}%
\begin{ocamlindent}Constructor argument with \ocamlinlinecode{global} modality.\end{ocamlindent}%
\ocamlcodefragment{| \ocamltag{constructor}{B} : (int \ocamltag{arrow}{$\rightarrow$} int) @@ portable \ocamltag{arrow}{$\rightarrow$} [ `b ] \hyperref[Oxcaml--type-modalities_gadt]{\ocamlinlinecode{modalities\_\allowbreak{}gadt}}}\label{Oxcaml--type-modalities_gadt.B}%
\begin{ocamlindent}Function constructor argument with modality.\end{ocamlindent}%
\ocamlcodefragment{| \ocamltag{constructor}{C} : int * string @@ portable \ocamltag{arrow}{$\rightarrow$} [ `c ] \hyperref[Oxcaml--type-modalities_gadt]{\ocamlinlinecode{modalities\_\allowbreak{}gadt}}}\label{Oxcaml--type-modalities_gadt.C}%
\begin{ocamlindent}Tuple constructor argument with modality.\end{ocamlindent}%
\ocamlcodefragment{| \ocamltag{constructor}{D} : int @@ portable * string @@ global \ocamltag{arrow}{$\rightarrow$} [ `d ] \hyperref[Oxcaml--type-modalities_gadt]{\ocamlinlinecode{modalities\_\allowbreak{}gadt}}}\label{Oxcaml--type-modalities_gadt.D}%
\begin{ocamlindent}Per-element modalities in a constructor tuple.\end{ocamlindent}%
\ocamlcodefragment{| \ocamltag{constructor}{E} : \{}\\
\begin{ocamltabular}{p{1.000\textwidth}}\ocamlinlinecode{x : int @@ portable;\allowbreak{}}\label{Oxcaml--type-modalities_gadt.x}\\
\ocamlinlinecode{y : string @@ global;\allowbreak{}}\label{Oxcaml--type-modalities_gadt.y}\\
\end{ocamltabular}%
\\
\ocamlcodefragment{\} \ocamltag{arrow}{$\rightarrow$} [ `e ] \hyperref[Oxcaml--type-modalities_gadt]{\ocamlinlinecode{modalities\_\allowbreak{}gadt}}}\label{Oxcaml--type-modalities_gadt.E}%
\begin{ocamlindent}Per-element modalities in a constructor record.\end{ocamlindent}%
\ocamlcodefragment{| \ocamltag{constructor}{F} : [ `f ] \hyperref[Oxcaml--type-modalities_gadt]{\ocamlinlinecode{modalities\_\allowbreak{}gadt}}}\label{Oxcaml--type-modalities_gadt.F}%
\begin{ocamlindent}Constant constructor.\end{ocamlindent}%
\end{ocamlindent}%
\subsubsection{Modalities on values\label{Oxcaml--modalities-on-values}}%
\label{Oxcaml--val-portable_fn}\ocamlcodefragment{\ocamltag{keyword}{val} portable\_\allowbreak{}fn : int \ocamltag{arrow}{$\rightarrow$} int @@ portable}\begin{ocamlindent}Value with \ocamlinlinecode{portable} modality.\end{ocamlindent}%
\medbreak
\subsubsection{Modalities on module declarations\label{Oxcaml--modalities-on-module-declarations}}%
\label{Oxcaml--module-type-S}\ocamlcodefragment{\ocamltag{keyword}{module} \ocamltag{keyword}{type} \hyperref[Oxcaml-module-type-S]{\ocamlinlinecode{S}}}\label{Oxcaml-module-type-S}\ocamlcodefragment{ = \ocamltag{keyword}{sig}}\begin{ocamlindent}\label{Oxcaml-module-type-S--type-s}\ocamlcodefragment{\ocamltag{keyword}{type} s = \{}\\
\begin{ocamltabular}{p{1.000\textwidth}}\ocamlinlinecode{a : int;\allowbreak{}}\label{Oxcaml-module-type-S--type-s.a}\\
\end{ocamltabular}%
\\
\ocamlcodefragment{\}}\\
\label{Oxcaml-module-type-S--val-x}\ocamlcodefragment{\ocamltag{keyword}{val} x : int}\\
\label{Oxcaml-module-type-S--val-f}\ocamlcodefragment{\ocamltag{keyword}{val} f : string \ocamltag{arrow}{$\rightarrow$} bool}\\
\label{Oxcaml-module-type-S--val-portable}\ocamlcodefragment{\ocamltag{keyword}{val} portable : string \ocamltag{arrow}{$\rightarrow$} string array @@ portable}\\
\label{Oxcaml-module-type-S--val-contended}\ocamlcodefragment{\ocamltag{keyword}{val} contended : string \ocamltag{arrow}{$\rightarrow$} bytes @@ contended}\\
\ocamlinlinecode{uncontended} and \ocamlinlinecode{nonportable} are the defaults (not rendered).

\label{Oxcaml-module-type-S--val-uncontended}\ocamlcodefragment{\ocamltag{keyword}{val} uncontended : string \ocamltag{arrow}{$\rightarrow$} bytes}\\
\label{Oxcaml-module-type-S--val-nonportable}\ocamlcodefragment{\ocamltag{keyword}{val} nonportable : string \ocamltag{arrow}{$\rightarrow$} string array}\\
\end{ocamlindent}%
\ocamlcodefragment{\ocamltag{keyword}{end}}\\
\label{Oxcaml--module-M1}\ocamlcodefragment{\ocamltag{keyword}{module} \hyperref[Oxcaml-M1]{\ocamlinlinecode{M1}}}\ocamlcodefragment{ : \hyperref[Oxcaml-module-type-S]{\ocamlinlinecode{S}}}\begin{ocamlindent}Module without modality.\end{ocamlindent}%
\medbreak
\label{Oxcaml--module-M2}\ocamlcodefragment{\ocamltag{keyword}{module} \hyperref[Oxcaml-M2]{\ocamlinlinecode{M2}}}\label{Oxcaml-M2}\ocamlcodefragment{ : \ocamltag{keyword}{sig}}\begin{ocamlindent}\label{Oxcaml-M2--type-s}\ocamlcodefragment{\ocamltag{keyword}{type} s : immutable\_\allowbreak{}data = \{}\\
\begin{ocamltabular}{p{1.000\textwidth}}\ocamlinlinecode{a : int;\allowbreak{}}\label{Oxcaml-M2--type-s.a}\\
\end{ocamltabular}%
\\
\ocamlcodefragment{\}}\\
\label{Oxcaml-M2--val-x}\ocamlcodefragment{\ocamltag{keyword}{val} x : int @@ portable}\\
\label{Oxcaml-M2--val-f}\ocamlcodefragment{\ocamltag{keyword}{val} f : string \ocamltag{arrow}{$\rightarrow$} bool @@ portable}\\
\label{Oxcaml-M2--val-portable}\ocamlcodefragment{\ocamltag{keyword}{val} portable : string \ocamltag{arrow}{$\rightarrow$} string array @@ portable}\\
\label{Oxcaml-M2--val-contended}\ocamlcodefragment{\ocamltag{keyword}{val} contended : string \ocamltag{arrow}{$\rightarrow$} bytes @@ portable contended}\\
\label{Oxcaml-M2--val-uncontended}\ocamlcodefragment{\ocamltag{keyword}{val} uncontended : string \ocamltag{arrow}{$\rightarrow$} bytes @@ portable}\\
\label{Oxcaml-M2--val-nonportable}\ocamlcodefragment{\ocamltag{keyword}{val} nonportable : string \ocamltag{arrow}{$\rightarrow$} string array @@ portable}\\
\end{ocamlindent}%
\ocamlcodefragment{\ocamltag{keyword}{end}}\begin{ocamlindent}Module with \ocamlinlinecode{portable} modality. The modality is applied to all value members of \ocamlinlinecode{M2}.\end{ocamlindent}%
\medbreak
\label{Oxcaml--module-M3}\ocamlcodefragment{\ocamltag{keyword}{module} \hyperref[Oxcaml-M3]{\ocamlinlinecode{M3}}}\label{Oxcaml-M3}\ocamlcodefragment{ : \ocamltag{keyword}{sig}}\begin{ocamlindent}\label{Oxcaml-M3--type-s}\ocamlcodefragment{\ocamltag{keyword}{type} s}\\
\label{Oxcaml-M3--val-f}\ocamlcodefragment{\ocamltag{keyword}{val} f : string \ocamltag{arrow}{$\rightarrow$} bool @@ contended}\\
\label{Oxcaml-M3--val-portable}\ocamlcodefragment{\ocamltag{keyword}{val} portable : string \ocamltag{arrow}{$\rightarrow$} string array @@ portable contended}\\
\label{Oxcaml-M3--val-nonportable}\ocamlcodefragment{\ocamltag{keyword}{val} nonportable : string \ocamltag{arrow}{$\rightarrow$} string array @@ contended}\\
\label{Oxcaml-M3--val-uncontended}\ocamlcodefragment{\ocamltag{keyword}{val} uncontended : string \ocamltag{arrow}{$\rightarrow$} bytes}\\
\end{ocamlindent}%
\ocamlcodefragment{\ocamltag{keyword}{end}}\begin{ocamlindent}\ocamlinlinecode{contended} modality applied to all definitions in the module, except the ones which have already specified this axis.\end{ocamlindent}%
\medbreak

\input{Oxcaml.M1.tex}
